---
title: "Course Notes Day 1"
author: "Martin Morgan"
date: "10/5/2015"
output: html_document
---

The following code chunks demonstrate basic R functionality. Some key points are:

- R is _vectorized_. Vectorized versions of calculations are 'fast'.
  (`sapply()` is actually iteration, not vectorization).
- Functions can be invoked with named or unnamed arguments. Named
  arguments are matched first. Unnamed arguments assigned left-to-right.
- Arguments can have default values
- Use `?rnorm` for help. Run help examples with `example(rnorm)`

```{r vectors-and-functions}
x = rnorm(1000)
y = x + rnorm(1000, sd=.5)
mean(x)
mean(y)
```

Vectors such as `x` and `y` can be combined into _objects_ such as 
`data.frame()`. Objects are subject to _introspection_.

```{r objects-data.frame}
df = data.frame(x=x, y=y)
class(df)
dim(df)
length(df)
```

An object helps to

- coordinate different components of the same data
- New 'methods' available to operate on the object, e.g., `dim()`

```{r methods}
fit <- lm(y ~ x, df)
anova(fit)
```

```{r visualize}
plot(y ~ x, df)
abline(fit)
```

What can I do with objects?

- Discover methods, with `methods(class="lm")` or `methods("anova")`
- `anova.lm` is an example of an "S3" method
    - Object of class 'lm'
    - `anova()`: generic
    - `anova.lm()`: method
- S3 methods can be viewed with `getAnywhere("anova.lm")` or
  `stats:::anova.lm`
- `?plot` provides help on the generic, but `?plot.lm` provides help
  on the method.

What is an S3 class?

- just a structure with a `class` attribute
- S3 methods are just plain-old-functions names as generic.class

```{r our-class}
obj = structure(list(), class="ourclass")
print.ourclass = function(x, ...) {
  cat("I'm an object of class:", class(x), "\n")
}
anotherobj = structure(list(), class=c("anotherclass", "ourclass"))
```

S4 classes are used in Bioconductor
- Classes defined in packages
- Objects created with 'constructors', e.g., `DNAStringSet()`
- Discover methods with `methods(class="DNAStringSet")`. S4 methods are
  presented as `generic,classA-method`, maybe with multiple classes
- Help, e.g., `?"length,XVectorList-method"`
- Discover class structure with `?getClass()`; `selectMethod()` is
  useful for finding the method

```{r Biostrings}
library(Biostrings)
dna = DNAStringSet(c("AACAT", "CTGGACA"))
```

S4 classes, generics and methods. S4 inheritance.

```{r our-S4}
.Person = setClass("Person", 
                   representation(name="character", age="numeric"))

setGeneric("name", function(object) standardGeneric("name"))

setMethod("name", "Person", function(object) {
  object@name
})

setGeneric("age", function(object) standardGeneric("age"))

setMethod("age", "Person", function(object) {
  object@age
})

setMethod("show", "Person", function(object) {
  cat("I'm a:", class(object), "\n")
  cat("name:", name(object), "\n")
  cat("age:", age(object), "\n")
})

.Employee = setClass("Employee", representation(job="character"),
                     contains="Person")
```

# Writing efficient code

Three points
- Correct more important than speed
- Understandable more important than speed
- Robust more important than speed

```{r inefficient-to-efficient}
## naive. quadratic -- time scales as n^2
f1 =function(n) {
  x = NULL
  for (i in 1:n)
    x = c(x, i)    # copies 1 + 2 + 3 + = n (n - 1) / 2 elements
  x
}

## 'pre-allocate and fill', linear scaling
f2 = function(n) {
  x = integer(n)
  for (i in 1:n)
    x[i] = i
  x
}

identical(f1(10), f2(10))

## not robust!
f1(0)

f3 = function(n) {
  x = integer(n)
  for (i in seq_len(n))
    x[i] = i
  x
}

## but f3() is more complicated than it needs to be
f4 = function(n) {
  sapply(seq_len(n), function(i) i)
}

## but f4() is an iteration, when a simple vectorized call will do
f5 = function(n) {
  seq_len(n)
}

## use the microbenchmark package to calculate multiple timings
library(microbenchmark)
microbenchmark(f4(1000), f5(1000))
```

# Aside: environments and scope

```{r bank-account}
account = function(initial_deposit) {
  ## every function has an _environment_. Every environment has a
  ## parent. The parent of a function's environment is the
  ## environment in which the function was called
  balance <- initial_deposit
  ## 'balance' is a symbol defined in the function's environment
  ## with value 'initial_deposit'
  
  list(getbalance=function() {
    ## this function also has an environment. It's parent is the
    ## environment of the 'account' function
    ## 'balance' isn't found in the environment of getbalance(), so
    ## R looks in the parent environment
    balance
  }, deposit=function(amt) {
    ## <<- says 'assign to an existing symbol in one of the 
    ## parent environments'
    balance <<- balance + amt
  }, withdraw=function(amt) {
    if (amt > balance)
      stop("insufficient funds")
    balance <<- balance - amt
    amt
  })
}
```
