---
title: "7. ChIP-Seq for Understanding Gene Regulation"
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
vignette: >
  % \VignetteIndexEntry{7. ChIP-Seq For Understanding Gene Regulation}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE, messages=FALSE, warnings=FALSE}
suppressPackageStartupMessages({})
```

Author: Martin Morgan (<a
  href="mailto:mtmorgan@fredhutch.org">mtmorgan@fredhutch.org</a>)<br/ >
Date: 5-9 October, 2015<br />

The material in this course requires R version 3.2 and Bioconductor
version 3.1

```{r configure-test}
stopifnot(
    getRversion() >= '3.2' && getRversion() < '3.3',
    BiocInstaller::biocVersion() == "3.1"
)
```

# Resources

Acknowledgements

- Core (Seattle): Sonali Arora, Marc Carlson, Nate Hayden, Jim Hester,
  Valerie Obenchain, Herv&eacute; Pag&egrave;s, Paul Shannon, Dan
  Tenenbaum.

- The research reported in this presentation was supported by the
  National Cancer Institute and the National Human Genome Research
  Institute of the National Institutes of Health under Award numbers
  U24CA180996 and U41HG004059, and the National Science Foundation
  under Award number 1247813. The content is solely the responsibility
  of the authors and does not necessarily represent the official views
  of the National Institutes of Health or the National Science
  Foundation.

## `sessionInfo()`

```{r sessionInfo}
sessionInfo()
```
